### 2019-01-04 revisions/review-responses.tex

                        In fact, SaltProc fully removes
                        all of these elements every 3435 days (not a small mass fraction every 3 days)
                        which causes the multiplication factor to jump by approximately 450
                        pcm, and limits using the batch approach for online reprocessing simulations.
                        In future versions of SaltProc this drawback will be eliminated by removing
                        elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
                         Cs, Ba, Eu). In that approach, chemistry models will inform separation
                         efficiencies for each reprocessing group and removal will optionally be spread more
                         evenly across the cycle time.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                Thank you for the recommendation. Atom density was chosen for 
                publication-to-publication comparison (e.g. Park \emph{et al.} and 
                Betzler \emph{et al.}
                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
                be more understandable for the reader and will be added in a future releases.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, Fig 9: What are the wiggles and dips , especially 
        seen for Np235?
        \begin{solution}
		        Explanation of this phenomenon has been added as follows:

                          ``Small dips in neptunium and plutonium number density 
                          every 16 years are caused by removing $^{237}$Np and 
                          $^{242}$Pu (included in Processing group ``Higher 
                          nuclides'', see Table~3
                          which decays into $^{235}$Np and $^{239}$Pu, 
                          respectively.''
        \end{solution}

### 2019-01-04 revisions/review-responses.tex

                The current version of SaltProc only allows 100\% separation 
                efficiency for either specific elements or groups of elements 
                (e.g. Processing Groups as described in 
				Table~\ref{tab:reprocessing_list}) at the end of the specific 
				cycle time. This simplification neglects the reality that 
				the salt spends appreciable time out of the core, in the 
				primary loop pipes and the heat exchanger.

				This approach works well for fast-removing elements (gases, 
				noble metals, protactinium) which should be removed each 
				depletion step. Unfortunately, for the elements with longer 
				cycle times (i.e. rare earths should be removed every 50 days) 
				this simplified approach leads to oscillatory behavior of all
				major parameters. In future releases of SaltProc, this drawback 
				will be eliminated by removing elements with longer cycle times 
				using different method: only mass fraction (calculated separately 
				for each reprocessing group) will be removed each depletion step 
				or batch (e.g. 3 days in the current work).
        \end{solution}

        %---------------------------------------------------------------------

        \question \label{osc} The oscillatory behavior shown in Fig. 7 on the time scale of 
        months/years is hard to explain. Is this because the fission product 
        with longer residence time are batch-wise removed at their ``effective 
        cycle time''? In case, why not to remove part of them at every depletion 
        step?  
        \begin{solution}
                Yes, the oscillation happened because the fission products 
                with longer residence time are removed at the end of cycle time. We 
                definitely will take your advice and improve the code in future 
                releases. The following text has been added to clarify this issue:

@@

        \question Are you considering the effect of the gradual poisoning of 
        the graphite with fission products? If not, it would be worthwhile 
        briefly discussing its effect.
        \begin{solution}
                This passage has been added:

				$^{135}$Xe is a strong poison to the reactor, and some 
				fraction of this gas is absorbed by graphite during MSBR
				operation. ORNL calculations shown that for unsealed commercial 
				graphite with helium permeability 10$^{-5}$ cm$^2$/s the 
				calculated poison fraction is less than 2\% \cite{robertson_conceptual_1971}. 
				This parameter can be improved by using experimental graphites 
				or by applying sealing technology. The effect of the gradual 
				poisoning of the core graphite with xenon is not treated here.
        \end{solution}

        %---------------------------------------------------------------------

        \question In the manuscript it is not always clear when the authors 
        refer to numerical approximations of physical situations. For instance, 
        the authors write ``Figure 16 demonstrates that batch-wise removal of 
        strong absorbers every 3 days did not necessarily leads to fluctuation 
        in results but rare earth elements 480 removal every 50 days causes an 
        approximately 600 pcm jump in reactivity.'' These 600 pcm are an effect 
        of a numerical approximation, but the way things are presented can be 
        confusing to the reader. Please try to explicitly separate physical and 
        numerical effects. And try to related numerical effects to physical 
        effects. For instance, how does these numerical ``jumps'' affect the 
        results?  In this sense, why the batch-wise removal of strong absorbers 
        every 3 days  was not done? And why a fraction of rare earths  is not 
        removed every three days?
        \begin{solution}
                This sentence was quite unclear and we have rewritten it to 
                address your concerns. Effectively these simulations exactly 
                simulated the batch-wise refuelling detailed in the Robertson 
                design document, while a more realistic approach would give 
                smooth behavior. A description of the changes to the text 
                appears in solution \ref{osc}.
        \end{solution}

### 2019-01-05 abstract.tex
energy -> energy technologies

In the search for new ways to generate carbon-free, reliable base-load power, 
interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
with multiple new companies pursuing commercialization of \gls{MSR} 
designs. To further 
develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
fueled \gls{MSR} depletion and fuel processing. However, most 
contemporary nuclear reactor physics software is unable to perform high-fidelity 
full-core depletion calculations for a reactor design with online reprocessing. This paper 
introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
SERPENT2 to simulate \gls{MSR} online reprocessing by modeling the changing 
isotopic composition of \gls{MSR} fuel salt. This work demonstrates SaltProc capabilities
for a full-core, high-fidelity model of the commercial \gls{MSBR} 
concept and verifies these results to results in the literature from 
independent, lower-fidelity analyses.

>>>>

In the search for new ways to generate carbon-free, reliable base-load power, 
interest in advanced nuclear energy technologies and particularly \glspl{MSR} has resurged, 
with multiple new companies pursuing commercialization of \gls{MSR} 
designs. To further 
develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
fueled \gls{MSR} depletion and fuel processing. However, most 
contemporary nuclear reactor physics software is unable to perform high-fidelity 
full-core depletion calculations for a reactor design with online reprocessing. This paper 
introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
SERPENT2 to simulate \gls{MSR} online reprocessing by modeling the changing 
isotopic composition of \gls{MSR} fuel salt. This work demonstrates SaltProc capabilities
for a full-core, high-fidelity model of the commercial \gls{MSBR} 
concept and verifies these results to results in the literature from 
independent, lower-fidelity analyses.
